Dissociation between vertebrae number and body size in Australian blindsnakes

### 2024-08-23 manuscript.Rmd
small adjustments

***[Discuss/speculate why vertebrae ratio is correlated with annual mean temperature and soil bulk density]***

Both mean annual temperature and soil bulk density were significant predictors of vertebrae ratio but in different directions. Mean annual temperature has been shown to be a good proxy for ecological factors relevant to squamates [@coxEvolutionary2015;@pieEvolution2017;@wiensDiversity2013]. However, temperature has also been shown to directly influence multiple axes of reptile development [@nobleDevelopmental2018;@boothInfluence2006;@feinerDevelopmental2018]. Vertebral development (somitogenesis) and homeotic (*Hox* gene) regulation may thus be affected by variations in incubation conditions [@martin-del-campoHox2018]. However, we currently lack knowledge about egg-laying behaviour and how temperature affects the development of blindsnake embryos. Common garden experiments across different species of blindsnakes may be able to shed light on whether variation in incubation temperature and consequently, the rate of development may alter the number of vertebrae formation during development. 
<!-- We would expect higher temperature to accelerate development (CITE anolis papers, turtles, etc), so less time for embryonic development.  -->

>>>>

### Vertebrae ratio and ecological variables
<!-- Discuss/speculate why vertebrae ratio is correlated with annual mean temperature and soil bulk density]*** -->

Both mean annual temperature and soil bulk density were significant predictors of vertebrae ratio but in different directions.

We found that species that occupy warmer environments has greater vertebrae ratio than those in cooler places.

Mean annual temperature has been shown to be a good proxy for ecological factors relevant to squamates [@coxEvolutionary2015;@pieEvolution2017;@wiensDiversity2013]. Temperature also directly influence multiple axes of reptile development [@nobleDevelopmental2018;@boothInfluence2006;@feinerDevelopmental2018]. Vertebral development (somitogenesis) and homeotic (*Hox* gene) regulation may thus be affected by variations in incubation conditions [@martin-del-campoHox2018]. However, we currently lack knowledge about egg-laying behaviour and how temperature affects the development of blindsnake embryos. Common garden experiments across different species of blindsnakes may be able to shed light on whether variation in incubation temperature and consequently, the rate of development may alter the number of vertebrae formation during development. 
<!-- We would expect higher temperature to accelerate development (CITE anolis papers, turtles, etc), so less time for embryonic development.  -->
